Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-07-15 sports_analytics.Rmd
chess

```{r chess-startup, fig.cap="The starting chess board printed via the \\pkg{chess} package."}
#library(chess)
#Sys.setenv(RETICULATE_PYTHON = "my_env/bin/python3")
#game() %>% plot()
```

>>>>

```{r chess-startup, fig.cap="The starting chess board printed via the \\pkg{chess} package."}
# library(chess)
# Sys.setenv(RETICULATE_PYTHON = "my_env/bin/python3")
# game() %>% plot()

# we could plot greg's chess moves
# doesn't work for me... python/reticulate issues
# library(chessR)
# greg <- get_raw_chessdotcom(usernames = "fatgreggy",
#                             year_month = "202206")
# m <- extract_moves_as_game(greg[1, ])
# plot_moves(m)
```
